An Embedding Framework for Consistent Polyhedral Surrogates

### 2021-08-04 poly-embed-journal/poly-embed-journal.tex
lovasz

In fact, this example is typical: % using our embedding framework, and characterizing when $0\in\reals^2$ is an embedded point,
one can show that $L^f$ is consistent if and only if $f_{1,2} = f_1 + f_2$.
Moreover, in this linear case, which corresponds to $f$ being \emph{modular}, the Lov\'asz hinge reduces to weighted Hamming loss, which is trivially consistent from the consistency of hinge loss for 0-1 loss.
In \S~\ref{app:lovasz}, we generalize this observation for all $k$.
\begin{theorem}
	Let $f$ be submodular, normalized, and increasing.
	Then $(L^f,\psi)$ is consistent if and only if $f$ is modular.
\end{theorem}
In other words, even for $k>2$, the only consistent Lov\'asz hinge is weighted Hamming loss.
This result casts doubt on the practical effectiveness of the Lov\'asz hinge as a surrogate for $\ell^f$.

In light of this negative result, together with the fact that every polyhedral surrogate embeds some target loss (Theorem~\ref{thm:poly-embeds-discrete}), we now turn to the question: what target problem, then, \emph{is} the Lov\'asz hinge consistent for?
We show in \S~\ref{app:lovasz} that the answer is a variant of abstain loss where one can abstain on a set of labels $B\subseteq[k]$.
Recall that the symmetric difference is defined by $S\triangle T = (S\setminus T) \cup (T\setminus S)$.
\begin{theorem}
	Let $\hat\ell^f:\hat\R\times\Y\to\reals_+$, where $\hat\R = \{(A,B) \in 2^{[k]} \times 2^{[k]}: A\cap B=\emptyset\}$, be given by
	\begin{equation}
	\hat\ell^f((A,B),S) = f(A\triangle S\setminus B) + f(A\triangle S\cup B)~.
	\end{equation}
	Then the Lov\'asz hinge $L^f$ embeds $\hat\ell^f$.
  Moreover, the embedding is tight whenever $f$ is strictly submodular.
\end{theorem}
\raf{Something about how this could actually be a useful target and surrogate, provided you actually link from the surrogate to the target and not ignore $B$.}

@@

From well-known facts about the Lov\'asz extension (see Lemma~\ref{lem:lovasz-trim} below), $L^f$ is certainly polyhedral, and thus by our framework we know it must embed a discrete loss $\hat\ell^f$, which may or may not be the same as $\ell^f$.
As with the top-$k$ example, we begin our analysis by calculating $\hat\ell^f$.

Let $\Gamma^f = \prop{L^f}$ and $\U = \{-1,0,1\}^k$.
Note that, for disjoint sets $A,B \subseteq N$, we have $\chi_A + \ones_B \in \U$, which at coordinate $i$ evaluates to $1$ for $i\in A$, $0$ for $i\in B$, and $-1$ otherwise.
Moreover, every point in $\U$ can be uniquely described in this way.
Finally, observe $\chi_A + \ones_B = \chi_A \odot \ones_{N\setminus B}$.

We will show that for every distribution $p$, an element of $\U$ is always represented in the minimizers of $L^f$, i.e., $\Gamma^f(p)$.
First, we show that we may restrict to the filled hypercube $[-1,1]^k$ without loss of generality.

\begin{lemma}
	\label{lem:lovasz-cube}
	Let $f:2^N\to\reals_+$ be increasing and normalized.
	Then for all $p\in\simplex$, $\Gamma(p) \cap [-1,1]^k \neq \emptyset$.
\end{lemma}
\begin{proof}
	Let $u\in\Gamma^f(p)$ such that $|u_i|>1$ for some $i\in [k]$, and furthermore suppose $|u_i|$ is the smallest value among all such coordinates, i.e., $|u_i| = \min\{|u_j| : |u_j| > 1\}$.
	We show that $u'\in\Gamma^f(p)$ where $u'_j = u_j$ for $j\neq i$ and $u'_i = \sgn(u_i)$ so that $|u'_i|=1$; the result then follows by iterating this argument until there are no entries with $|u_i|>1$.
	In fact, we will show the stronger statement that for all $S\in\Y$, $L^f(u',S) \leq L^f(u,S)$.
	Let $w = \ones - u\odot \chi_S$ and $w' = \ones - u'\odot \chi_S$, and note that $L^f(u,S) = F(w_+)$ and $L^f(u',S) = F(w'_+)$.

@@

\begin{lemma}
	\label{lem:lovasz-trim}
	Let $\Gamma = \prop{L^f}$.
	Then for all $p\in\simplex$, $\Gamma(p) \cap \U \neq \emptyset$.
\end{lemma}
\begin{proof}
	We will construct polytopes $P^A_\pi \subseteq [-1,1]^k$ for every set $A\subseteq N$ and permutation $\pi \in N^N$, satisfying three conditions: (i) these polytopes cover the hypercube, meaning $\cup_{A,\pi} P^A_\pi = [-1,1]^k$, (ii) $P^A_\pi$ is the convex hull of points in $\U$, and (iii) for all $S\subseteq N$, $L(\cdot,S)$ is linear on $P^A_\pi$.
	The result will then follow, as $L(\cdot;p)$ will be also linear on each $P^A_\pi$, and thus minimized at a vertex.

	To begin, let us recall the polyhedra on which the Lov\'asz extension is linear; for any permutation $\pi$, define $P_\pi = \{u\in\reals^k : u_{\pi_1} \geq \cdots \geq u_{\pi_k}\}$.
	It is clear from the definition that $F$ is linear on $P_\pi$; see also Equation 3.1, and ``Linear interpolation on simplices'' (pg.\ 167) in \citet{bach2013learning}.
	We will use these polyhedra to identify the regions where $L(\cdot,S)$ is linear simultaneously for all outcomes $S\in\Y$.
	For any $A\subseteq N$ and permutation $\pi$, let
	\begin{equation}
	\label{eq:poly-pi}
	P^A_\pi = \{u\in[-1,1]^k : u \odot \chi_A \in P_\pi \cap \reals^k_+\}~.
	\end{equation}
	That is, $P^A_\pi$ contains all points $u$ such that $u \odot \chi_A$ is nonnegative (meaning $\sgn(u)$ matches $\chi_A$, breaking ties at $0$ favorably) and such that the coordinates of $u \odot \chi_A$ are in increasing order according to $\pi$.

@@

	Finally, for condition (iii), fix a subset $A\subseteq N$ and permutation $\pi$.
	For each outcome $S\subseteq N$, we will construct an alternate permutation $\pi^S$ such that for all $u\in P^A_\pi$ we have $\ones - u\odot\chi_S \in P_{\pi^S}$.
	As $F$ is linear on $P_{\pi'}$ for all permutations $\pi'$, we will conclude that for any fixed subset $S$ the loss $L(u,S) = F(\ones - u\odot\chi_S)$ will be linear in $u$ on $P^A_\pi$.

@@

We can now see that $L^f$ embeds the loss given by $L^f$ restricted to $\U$, as $\U$ is a finite set.
In fact, we can write this loss entirely in terms of $f$ itself.

@@

From the form~\eqref{eq:lovasz-embeds}, we see that $\hat\ell^f$ matches $2\ell$ when $B=\emptyset$, just as hinge loss embeds twice 0-1 loss.
When $B$ is nonempty, it acts as an ``abstain set'', guaranteeing some loss in the second term, but removing errors in the first term.

@@

\begin{lemma}
	\label{lem:bar-f}
	Let $f$ be submodular and normalized.
	Then $\bar f \geq f(N)/2$, and $f$ is modular if and only if $\bar f = f(N)/2$.
\end{lemma}
\begin{proof}
	The inequality follows from Lemma~\ref{lem:2-bar-f} with $B=\emptyset$.
	Next, note that if $f$ modular we trivially have $\bar f = f(N)/2$.
	If $f$ is submodular but not modular, we must have some $S\subseteq N$ and $i\in S$ such that $f(S) - f(S\setminus\{i\}) < f(\{i\})$.
	%\raft{I have a proof of this; will fill in later}
	By submodularity, we conclude that $f(N) - f(N\setminus\{i\}) < f(\{i\})$ as well; rearranging, $f(\{i\}) + f(N\setminus\{i\}) > f(N) = f(N) + f(\emptyset)$.
	Again examining the proof of Lemma~\ref{lem:2-bar-f}, we see that the first inequality must be strict, as we have one such $T\subseteq N$, namely $T=\{i\}$, for which the inequality in submodularity is strict.
\end{proof}

\begin{theorem}
	Let $f$ be submodular, normalized, and increasing.
	Then $(L^f,\sgn)$ is consistent if and only if $f$ is modular.
\end{theorem}
\begin{proof}
	If $f$ is modular, then $F$ is linear, and $L^f(\cdot;p)$ is linear on $[-1,1]^k$.
	We conclude that $L^f(\cdot;p)$ is minimized at a vertex of the hypercube, meaning $L^f$ embeds $2\ell^f$.
	(Equivalently, there is always an optimal report $(A,\emptyset)\in\hat\R$ for $\hat\ell^f$.)
	Calibration and consistency then follow.
	%\raft{Too informal; should flesh out---in particular, is there is easy way to see that $\sgn$ works using our construction?}

@@

	Define $\epsilon = \bar f / (2\bar f - f(N))$, which is strictly positive by Lemma~\ref{lem:bar-f} and submodularity of $f$.
	Let $p = (1-\epsilon) \bar p + \epsilon \delta_\emptyset$, where again $\bar p$ is the uniform distribution, and $\delta_\emptyset$ is the point distribution on $\emptyset$.
	From Lemma~\ref{lem:2-bar-f}, for all $A\subseteq N$ we have
	\begin{align*}
	\hat\ell^f((A,\emptyset);p)
	&= (1-\epsilon) 2 \bar f + \epsilon \, \hat\ell^f((A,\emptyset),\emptyset)\\
	&= (1-\epsilon) 2 \bar f + \epsilon \, 2f(A)\\
	&\geq (1-\epsilon)2 \bar f > f(N) = \hat\ell^f((\emptyset,N);p)~.
	\end{align*}
	As we have some report with strictly lower loss than all reports of the form $(A,\emptyset)$, we conclude that we must have some $(A,B) \in \prop{\hat\ell^f}(p)$ with $B\neq\emptyset$.
	We can also see that $\prop{\ell^f}(p) = \{\emptyset\}$ by the second equality and the fact that $\{\emptyset\} = \argmin_{S\subseteq N} f(S)$.

	Revisiting $L^f$, from Lemma~\ref{lem:lovasz-u} and the map between $\U$ and $\hat\R$, we have some $u\in\Gamma^f(p)$ which we can write $u = \chi_A + \ones_B$.
	Let $T\subseteq N$ such that $\chi_T = \sgn(u)$ after breaking ties, and note that $A \subseteq T \subseteq A\cup B$.
	If $T\neq\emptyset$, we are done, as by the above $\emptyset$ optimizes $\ell^f$, so we have violated calibration and therefore consistency.

	Otherwise, $T=\emptyset$, so $A=\emptyset$ as well.
	In this case, we will modify $p$ to put weight on $B\neq\emptyset$ instead of $\emptyset$, and will find that $u$ is still optimal for $L^f$, again violating calibration.
	To show optimality, let $c = L^f(u;p) = \risk{L^f}(p)$, and note that by symmetry of $L^f$, for any $S\subseteq N$ we have $c = \risk{L^f}(p^S)$ as well, where $p^S = (1-\epsilon)\bar p + \epsilon \delta_S$.
	%\raft{Too informal; should flesh out}
	In particular, this will hold for $p^B$.
	By Lemma~\ref{lem:lovasz-u}, we have
	$L^f(u,B) = f(\emptyset\triangle B\setminus B) + f(\emptyset\triangle B\cup B) = f(\overline B) + f(N) = f(\emptyset\triangle \emptyset\setminus B) + f(\emptyset\triangle \emptyset\cup B) = L^f(u,\emptyset)$.
        \raft{Wait, I think $f(\overline B) + f(N)$ should be $f(\emptyset) + f(B)$}
	Thus, $L^f(u,p^B) = (1-\epsilon) L^f(u,\bar p) + \epsilon L^f(u,B) = (1-\epsilon) L^f(u,\bar p) + \epsilon L^f(u,\emptyset) = L^f(u,p) = c$, so $u$ is still optimal.
	As $\chi_B \neq \chi_T = \sgn(u)$, we are done.
\end{proof}

\subsection{Tightness of the embedding}

>>>>

In fact, this example is typical: % using our embedding framework, and characterizing when $0\in\reals^2$ is an embedded point,
one can show that $L^f$ is consistent if and only if $f_{1,2} = f_1 + f_2$.
Moreover, in this linear case, which corresponds to $f$ being \emph{modular}, the Lov\'asz hinge reduces to weighted Hamming loss, which is trivially consistent from the consistency of hinge loss for 0-1 loss.
In \S~\ref{app:lovasz}, we generalize this observation for all $k$.
\begin{theorem}\label{thm:lovasz-consistent-main}
	Let $f$ be submodular, normalized, and increasing.
	Then $(L^f,\psi)$ is consistent if and only if $f$ is modular.
\end{theorem}
In other words, even for $k>2$, the only consistent Lov\'asz hinge is weighted Hamming loss.
This result casts doubt on the practical effectiveness of the Lov\'asz hinge as a surrogate for $\ell^f$.

In light of this negative result, together with the fact that every polyhedral surrogate embeds some target loss (Theorem~\ref{thm:poly-embeds-discrete}), we now turn to the question: what target problem, then, \emph{is} the Lov\'asz hinge consistent for?
We show in \S~\ref{app:lovasz} that the answer is a variant of abstain loss where one can abstain on a set of labels $B\subseteq[k]$.
Recall that the symmetric difference is defined by $S\triangle T = (S\setminus T) \cup (T\setminus S)$.
\begin{theorem}\label{thm:lovasz-embed-main}
	Let $\hat\ell^f:\hat\R\times\Y\to\reals_+$, where $\hat\R = \{(A,B) \in 2^{[k]} \times 2^{[k]}: A\cap B=\emptyset\}$, be given by
	\begin{equation}
	\hat\ell^f((A,B),S) = f(A\triangle S\setminus B) + f(A\triangle S\cup B)~.
	\end{equation}
	Then the Lov\'asz hinge $L^f$ embeds $\hat\ell^f$.
  Moreover, the embedding is tight whenever $f$ is strictly submodular.
\end{theorem}
\raf{Something about how this could actually be a useful target and surrogate, provided you actually link from the surrogate to the target and not ignore $B$.}

@@

From well-known facts about the Lov\'asz extension (see Lemma~\ref{lem:lovasz-trim} below), $L^f$ is certainly polyhedral, and thus by our framework we know it must embed a discrete loss $\hat\ell^f$, which may or may not be the same as $\ell^f$.
We begin our analysis by calculating $\hat\ell^f$.

We will show that the set $\U = \{-1,0,1\}^k$ is representative for $L^f$.
Note that, for disjoint sets $A,B \subseteq N$, we have $\chi_A + \ones_B \in \U$, which at coordinate $i$ evaluates to $1$ for $i\in A$, $0$ for $i\in B$, and $-1$ otherwise.
Moreover, every point in $\U$ can be uniquely described in this way.
Finally, observe $\chi_A + \ones_B = \chi_A \odot \ones_{N\setminus B}$.

As a first step, we show that the filled hypercube $[-1,1]^k$ is representative.

\begin{lemma}
	\label{lem:lovasz-cube}
	For any increasing and normalized $f:2^N\to\reals_+$, the set $[-1,1]^k$ is representative for $L^f$.
	% Then for all $p\in\simplex$, $\Gamma(p) \cap [-1,1]^k \neq \emptyset$.
\end{lemma}
\begin{proof}
	Let $u\in\Gamma^f(p)$ such that $|u_i|>1$ for some $i\in [k]$, and furthermore suppose $|u_i|$ is the smallest value among all such coordinates, i.e., $|u_i| = \min\{|u_j| : |u_j| > 1\}$.
	We show that $u'\in\Gamma^f(p)$ where $u'_j = u_j$ for $j\neq i$ and $u'_i = \sgn(u_i)$ so that $|u'_i|=1$; the result then follows by iterating this argument until there are no entries with $|u_i|>1$.
	In fact, we will show the stronger statement that for all $S\in\Y$, $L^f(u',S) \leq L^f(u,S)$.
	Let $w = \ones - u\odot \chi_S$ and $w' = \ones - u'\odot \chi_S$, and note that $L^f(u,S) = F(w_+)$ and $L^f(u',S) = F(w'_+)$.

@@

\begin{lemma}
	\label{lem:lovasz-trim}
	For any increasing and normalized $f:2^N\to\reals_+$, the finite set $\U$ is representative for $L^f$.
\end{lemma}
\begin{proof}
	We will construct polytopes $P^A_\pi \subseteq [-1,1]^k$ for every set $A\subseteq N$ and permutation $\pi \in N^N$, satisfying three conditions: (i) these polytopes cover the hypercube, meaning $\cup_{A,\pi} P^A_\pi = [-1,1]^k$, (ii) $P^A_\pi$ is the convex hull of points in $\U$, and (iii) for all $S\subseteq N$, $L(\cdot,S)$ is affine on $P^A_\pi$.
	The result will then follow, as $L(\cdot;p)$ will be also affine on each $P^A_\pi$, and thus minimized at a vertex.

	To begin, let us recall the polyhedra on which the Lov\'asz extension is affine; for any permutation $\pi$, define $P_\pi = \{u\in\reals^k : u_{\pi_1} \geq \cdots \geq u_{\pi_k}\}$.
	It is clear from the definition that $F$ is affine on $P_\pi$; see also Equation 3.1, and ``Linear interpolation on simplices'' (pg.\ 167) in \citet{bach2013learning}.
	We will use these polyhedra to identify the regions where $L(\cdot,S)$ is affine simultaneously for all outcomes $S\in\Y$.
	For any $A\subseteq N$ and permutation $\pi$, let
	\begin{equation}
	\label{eq:poly-pi}
	P^A_\pi = \{u\in[-1,1]^k : u \odot \chi_A \in P_\pi \cap \reals^k_+\}~.
	\end{equation}
	That is, $P^A_\pi$ contains all points $u$ such that $u \odot \chi_A$ is nonnegative (meaning $\sgn(u)$ matches $\chi_A$, breaking ties at $0$ favorably) and such that the coordinates of $u \odot \chi_A$ are in increasing order according to $\pi$.

@@

	Finally, for condition (iii), fix a subset $A\subseteq N$ and permutation $\pi$.
	For each outcome $S\subseteq N$, we will construct an alternate permutation $\pi^S$ such that for all $u\in P^A_\pi$ we have $\ones - u\odot\chi_S \in P_{\pi^S}$.
	As $F$ is affine on $P_{\pi'}$ for all permutations $\pi'$, we will conclude that for any fixed subset $S$ the loss $L(u,S) = F(\ones - u\odot\chi_S)$ will be affine in $u$ on $P^A_\pi$.

@@

We can now see that $L^f$ embeds the loss given by $L^f$ restricted to $\U$, as $\U$ is a finite set.
In fact, we can write this loss entirely in terms of $f$ itself.
This statement proves the first part of Theorem~\ref{thm:lovasz-embed-main}; see \S~\ref{app:lovasz-tight} for when this embedding is tight.

@@

From the form~\eqref{eq:lovasz-embeds}, we see that $\hat\ell^f$ matches $2\ell^f$ when $B=\emptyset$, just as hinge loss embeds twice 0-1 loss.
When $B$ is nonempty, it acts as an ``abstain set'', guaranteeing some loss in the second term, but removing errors in the first term.

@@

\begin{lemma}
	\label{lem:bar-f}
	Let $f$ be submodular and normalized.
	Then $\bar f \geq f(N)/2$, and $\bar f = f(N)/2$ if and only if $f$ is modular.
\end{lemma}
\begin{proof}
	The inequality follows from Lemma~\ref{lem:2-bar-f} with $B=\emptyset$.
	Next, note that if $f$ modular we trivially have $\bar f = f(N)/2$.
	If $f$ is submodular but not modular, we must have some $S\subseteq N$ and $i\in S$ such that $f(S) - f(S\setminus\{i\}) < f(\{i\})$.
	%\raft{I have a proof of this; will fill in later}
	By submodularity, we conclude that $f(N) - f(N\setminus\{i\}) < f(\{i\})$ as well; rearranging, $f(\{i\}) + f(N\setminus\{i\}) > f(N) = f(N) + f(\emptyset)$.
	Again examining the proof of Lemma~\ref{lem:2-bar-f}, we see that the first inequality must be strict, as we have one such $T\subseteq N$, namely $T=\{i\}$, for which the inequality in submodularity is strict.
\end{proof}

We can now restate and prove Theorem~\ref{thm:lovasz-consistent-main}.
\begin{theorem}
	Let $f$ be submodular, normalized, and increasing.
	Then $(L^f,\sgn)$ is consistent if and only if $f$ is modular.
\end{theorem}
\begin{proof}
	If $f$ is modular, then $F$ is linear, and $L^f(\cdot;p)$ is linear on $[-1,1]^k$.
	We conclude that $L^f(\cdot;p)$ is minimized at a vertex of the hypercube, meaning $L^f$ embeds $2\ell^f$.
	(Equivalently, there is always an optimal report $(A,\emptyset)\in\hat\R$ for $\hat\ell^f$.)
	Calibration and consistency then follow.
	%\raft{Too informal; should flesh out---in particular, is there is easy way to see that $\sgn$ works using our construction?}

@@

	Define $\epsilon = \bar f / (2\bar f - f(N))$, which is strictly positive by Lemma~\ref{lem:bar-f} and submodularity of $f$.
	Let $p^S = (1-\epsilon) \bar p + \epsilon \delta_S$, where again $\bar p$ is the uniform distribution, and $\delta_S$ is the point distribution on $S$.
  We begin with $p^\emptyset$.
	From Lemma~\ref{lem:2-bar-f}, for all $A\subseteq N$ we have
	\begin{align*}
	\hat\ell^f((A,\emptyset);p^\emptyset)
	&= (1-\epsilon) 2 \bar f + \epsilon \, \hat\ell^f((A,\emptyset),\emptyset)\\
	&= (1-\epsilon) 2 \bar f + \epsilon \, 2f(A)\\
	&\geq (1-\epsilon)2 \bar f > f(N) = \hat\ell^f((\emptyset,N);p^\emptyset)~.
	\end{align*}
	As we have some report with strictly lower loss than all reports of the form $(A,\emptyset)$, we conclude that we must have some $(A,B) \in \prop{\hat\ell^f}(p^\emptyset)$ with $B\neq\emptyset$.
	We can also see that $\prop{\ell^f}(p^\emptyset) = \{\emptyset\}$ by the second equality, since $\ell^f(A,\cdot) = \hat\ell^f((A,\emptyset),\cdot)$ and $\{\emptyset\} = \argmin_{S\subseteq N} f(S)$.

	Now let $\Gamma^f = \prop{L^f}$.
  From Lemma~\ref{lem:lovasz-u} and the map between $\U$ and $\hat\R$, we have some $u\in\Gamma^f(p^\emptyset)$ which we can write $u = \chi_A + \ones_B$ for disjoint $A,B\subseteq N$.
	Let $T\subseteq N$ such that $\chi_T = \sgn(u)$ after breaking ties, and note that $A \subseteq T \subseteq A\cup B$.
	If $T\neq\emptyset$, we are done, as by the above $\emptyset$ optimizes $\ell^f$, so we have violated calibration and therefore consistency.
  Otherwise, $T=\emptyset$, so $A=\emptyset$ as well.
	In this case, we will shift to $p^B$, and show that $u\in\Gamma^f(p^B)$ as well, again violating calibration.

	To show optimality, let $c = L^f(u;p^\emptyset) = \risk{L^f}(p^\emptyset)$, and note that by symmetry of $L^f$, for any $S\subseteq N$ we have $c = \risk{L^f}(p^S)$ as well.
	%\raft{Too informal; should flesh out}
	In particular, we have $c = \risk{L^f}(p^B)$.
	By Lemma~\ref{lem:lovasz-u}, we have
	$L^f(u,B) = f(\emptyset\triangle B\setminus B) + f(\emptyset\triangle B\cup B) = f(\emptyset) + f(B) = f(\emptyset\triangle \emptyset\setminus B) + f(\emptyset\triangle \emptyset\cup B) = L^f(u,\emptyset)$.
  Thus, $L^f(u,p^B) = (1-\epsilon) L^f(u,\bar p) + \epsilon L^f(u,B) = (1-\epsilon) L^f(u,\bar p) + \epsilon L^f(u,\emptyset) = L^f(u,p^\emptyset) = c$.
  As $c=\risk{L^f}(p^B)$, we conclude $u\in\Gamma^f(p^B)$.
	Finally, as $\chi_B \neq \chi_T = \sgn(u)$, we are done.
\end{proof}

\subsection{Tightness of the embedding}
\label{app:lovasz-tight}
